Model

### 2019-09-10 stats/model.Rmd
add 100k model runs

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 50000,
                        burn = 25000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

sem_know_model <- readRDS("../saves/sem_know_model_variant2_50k.rds")

@@

saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k.rds")

>>>>

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 100000,
                        burn = 50000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 5000)
)

@@

sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k.rds")

@@

saveRDS(sem_know_model, "../saves/sem_know_model_variant1_100k.rds")
